%-------------------------------------
% Resume in LaTeX (XeLaTeX)
% Author:  Anthony Meza
% Base template by: HF Yuan
% Project: https://github.com/xyz-yuanhf/yuan-resume
% License: MIT
%------------------------------------

\documentclass[a4paper, 11pt]{article}
\usepackage{simpleresume}  % Style package

% --------------------  START  --------------------
\begin{document}

% -------------------- HEADING --------------------
\headerContact{(714) 552-2396}{ameza@mit.edu}{anthony-meza.github.io}
\headerName{Anthony Meza}
\headerTitle{Ph.D. Candidate}

% -------------------- RESEARCH INTERESTS --------------------
% \section{Research Interests}

% \skillListStart
% \justifying
% \hyphenpenalty=10000
% \exhyphenpenalty=10000
% \item My thesis is focused on past and future changes in global ocean circulation, with an emphasis on identifying the driving mechanisms and evaluating their detectability in observational records. Beyond my thesis work, I am broadly interested in all research that combine models and observations to advance our understanding of Earth's global and regional climate systems, particularly problems involving ocean dynamics, climate variability, and long-term climate change.\\
% \skillListEnd

% -------------------- EDUCATION --------------------
\section{Education}

\eduHeading
  {Massachusetts Institute of Technology \&\\ Woods Hole Oceanographic Institution}{Cambridge, MA}
  {Ph.D. in Physical Oceanography}{2021--Present}
\itemListStart
  \myItem{Advisor: Geoffrey Gebbie}
  \myItem{Thesis Committee: Henri Drake, Christopher Piecuch, Viviane de Menezes, Raffaele Ferrari}
\itemListEnd

\eduHeading
  {University of California, Irvine}{Irvine, CA}
  {B.S. in Mathematics, Concentration in Data Science}{2018--2021}

% -------------------- PUBLICATIONS --------------------
\section{Publications}

\pubListStart
\justifying
\pubItem{\textbf{Meza, A.}, \& Gebbie, G. (2025). Wind-driven mid-depth Pacific cooling in a dynamically consistent ocean state estimate. \textit{Journal of Geophysical Research: Oceans}. doi.org/10.1029/2025JC022462}
% \item \textbf{Meza, A.}, Drake, H. \& Gebbie, G. \textit{(In Prep)}. Projected Changes in Dense Shelf Water and their Abyssal Expression.
% \item \textbf{Meza, A.}, et al. \textit{(In Prep)}. 
% Detection of .
% \item \textbf{Meza, A.}, Bhuyan, P., Zheng, Z. \& Gebbie, G. \textit{(In Prep)}. Passive and Dynamic Contributions to Mean Ocean Temperature during the Last Glacial Maximum.
\pubListEnd

% -------------------- RESEARCH EXPERIENCE --------------------
\section{Research Experience}

\positionHeading[Graduate Research Assistant]
  {Woods Hole Oceanographic Institution}{Woods Hole, MA}{Sep 2021--Present}
\itemListStart
  \myItem{Tested causes of deep ocean cooling using global MITgcm simulations, supporting NASA efforts of global ocean modeling and data assimilation.}
  \myItem{Analyzed 40TB+ of high-resolution coupled climate model output to understand the connections between ocean circulation and dissolved chemicals in the ocean.}
  \myItem{Produced written reports, posters, and presentations to communicate findings to broader communities.}
    \myItem{Processed and analyzed 5TB+ of high-resolution ocean reanalysis data and found significant connections between near-shore sea surface temperature and extreme California precipitation events.}
  \myItem{Developed tools to analyze big climate data using Python and Julia.}
\itemListEnd

\positionHeading[Summer Intern]
  {Los Alamos National Laboratory}{Los Alamos, NM}{Jun 2021--Aug 2021}
\itemListStart
  \myItem{Implemented reduced-precision capabilities within the ocean component of the Energy Exascale Earth System Model.}
  \myItem{Found that reduced precision significantly reduced compute time but at cost of model skill.}
\itemListEnd

\positionHeading[Summer Intern]
  {Institute for Pure and Applied Mathematics}{Los Angeles, CA}{Jun 2020--Sep 2020}
\itemListStart
    \myItem{Designed and implemented reinforcement learning algorithms for adaptive packet routing in satellite network simulations.}
  \myItem{Empirical models were built in Python primarily using PyTorch and NetworkX.}
\itemListEnd

\section{Teaching Experience}

\ListStart
\justifying
\entryItem{Co-organizer and Instructor}{High Performance Computing and Data Analysis Workshop}{2024}
\entryItem{Calculus Instructor}{MIT-WHOI Joint Program Summer Math Refresher}{2024}
\entryItem{Partial Differential Equations Instructor}{MIT-WHOI Joint Program Summer Math Refresher}{2023}
\ListEnd
~

% -------------------- SERVICE AND LEADERSHIP --------------------
\section{Service \& Leaders
hip}

\ListStart
\justifying
\entryItem{Committee Member}{AMS Committee on Climate Variability and Change}{2024--Present}
\entryItem{Graduate Application Mentor}{Joint Program Applicant Support \& Knowledgebase}{2023--Present}
\entryItem{Physical Oceanography Representative}{WHOI Joint Program Student Representative}{2023--2024}
\entryItem{Conference Co-Organizer}{2023 Graduate Climate Conference}{2023}
\entryItem{At-Large Representative}{WHOI Joint Program Student Representative}{2022--2023}
\entryItem{Conference Co-Organizer}{2022 First Generation Summit}{2022}
\entryItem{Committee Member}{UC Irvine Mathematics Inclusive Excellence Committee}{2020--2021}
\ListEnd
~
% -------------------- Workshops & Summer Schools --------------------
\section{Workshops and Summer Schools Attended}

\ListStart
\justifying
\entryItem{CESM/MOM6 Regional Modeling Workshop}{NCAR Mesa Laboratory, Boulder, CO}{May 2025}
\entryItem{ECCO Summer School}{Asilomar Conference Center, Monterey, CA}{May 2025}
\entryItem{Tracer Mixing in Fluids Across Planetary Scales Summer School}{Brin Mathematics Research Center, College Park, MD}{Jul 2024}
\ListEnd
~

% -------------------- AWARDS & HONORS --------------------
\section{Awards and Honors Received}

\ListStart
\justifying
\entryItem{GEM Fellowship}{National Consortium of Graduate Degrees for Minorities in Engineers, MIT}{2021}
\entryItem{Rose Hills Scholarship}{Rose Hills Foundation, UC Irvine}{2020}
\entryItem{Rose Hills Scholarship}{Rose Hills Foundation, UC Irvine}{2019}
\entryItem{Bellettini Scholarship}{Maria Rebecca and Maureen Bellettini Fund, UC Irvine}{2019}
\entryItem{SCE STEM Scholarship}{Southern California Edison, UC Irvine}{2019}
\ListEnd
~

% -------------------- PRESENTATIONS --------------------
\section{Presentations}

\pubListStart
\justifying
\pubItem{\textbf{A. Meza}, G. Gebbie. ``Wind-driven mid-depth Pacific cooling in a dynamically consistent ocean state estimate'' ECCO Summer School, 19--30 May 2025, Asilomar Conference Center, Monterey, CA. \textit{Poster}.}
\pubItem{\textbf{A. Meza}, P. Bhuyan, Z. Zheng, G. Gebbie., M. Linz, J. Wenegrat. ``Surface to Bottom Connections in Earth's Ocean'' Tracer Mixing in Fluids Across Planetary Scales Summer School, 8--19 Jul 2024, Brin Mathematics Research Center, College Park, MD. \textit{Talk}.}
\pubItem{\textbf{A. Meza}, H. Seo. ``Associations Between Coastally Trapped Waves and Wintertime Precipitation in California'' Ocean Sciences Meeting, 18--23 Feb 2024, New Orleans, LA. \textit{Poster}.}
\pubItem{\textbf{A. Meza}, H. Seo. ``Associations Between Coastally Trapped Waves and Wintertime Precipitation in California'' Graduate Climate Conference, 1--3 Nov 2023, Marine Biological Laboratory, Woods Hole, MA. \textit{Poster}.}
\pubItem{\textbf{A. Meza}, G. Gebbie. ``Drivers of subsurface Pacific cooling in ECCOv4r4'' ECCO Annual Meeting 2023, 25 Jan 2023, University of Washington, Seattle, WA. \textit{Virtual Talk}.}
\pubItem{\textbf{A. Meza}, G. Gebbie. ``Drivers of mid-depth Pacific cooling trends in an ocean reanalysis'' AGU Fall Meeting 2022, 2--4 Nov 2023, Chicago, IL. \textit{Poster}.}
\pubItem{\textbf{A. Meza}, G. Gebbie. ``Drivers of mid-depth Pacific cooling trends in an ocean reanalysis'' Graduate Climate Conference, 31 Oct 2022, University of Washington, Seattle, WA. \textit{Poster}.}
\pubItem{{C. Tran}, \textbf{A. Meza}, H.L. Tung, H. Liu. ``A Reinforcement Learning Approach to Packet Routing on a Dynamic Network'' Joint Mathematics Meeting, 6--9 Jan 2021, Virtual. \textit{Virtual Talk}.}
\pubListEnd
~
% -------------------- SKILLS --------------------
% \sectionBlock{
% \section{Technical Skills}
% }{
% \skillListStart
% \justifying
% \item \emph{Programming Languages}: Python, Julia, MATLAB.
% \item \emph{Developer Tools}: Slurm, Unix, Git, Github, VS Code.
% \skillListEnd

% -------------------- PROFESSIONAL REFERENCES --------------------
\section{Professional References}
\begin{itemize}[leftmargin=0pt, label={}]
    \item Geoffrey Gebbie (ggebbie@whoi.edu)
    \item Henri Drake (hdrake@uci.edu)
    \item Christopher Piecuch (cpiecuch@whoi.edu)
\end{itemize}

\end{document}
